\section{Evaluation}
\label{sec:evaluation}
In this section we evaluate the chatbot tool we created for this project. We
use a set of questions to evaluate the performance of the chatbot. For question
we provide the best response from our chatbot along with a piece of context we
have from the documentation of the Fogify tool. This way we compare the results
of the chatbot in comparison with the context of the documentation. Below we
provide the set of questions we asked our chatbot.

\subsubsection*{Questions used in the evaluation stage}
\begin{enumerate}
    \item What is an action and how can i add an action using python code?
    \item What are some parameters that we specify in the Fogify emulator for
          network connectivity? Can you give me an example of yaml
          configuration?
    \item What are blueprints and what are their different variables? Can you
          also give me an example?
    \item How does Fofigy compose the network latency can you give me an
          example of configuration with the different variables in that yaml?
    \item Explain the different parameters of the blueprint.
    \item What are the performance metrics captured by Fogify. Can you give me
          the metric and a small description for it?
    \item Can a user add its own metrics to fogify? How can a user do that can
          you give me an example?
    \item How can someone interact with the emulated testbed?
    \item Can you give me an example in python code on how i can use the fogify
          SDK library to interact with the Fogify emulation tool?
\end{enumerate}

